The Precambrian paleogeography of Laurentia

### 2021-07-23 Manuscript/Laurentia_Paleogeo_Manuscript.tex
update Zenodo link

%%%%%%%%%%%%% Acknowledgements %%%%%%%%%%%%%
\footnotesize
\subsection*{Acknowledgements}
This work was supported by NSF CAREER Grant EAR-1847277. The manuscript benefited from reviews from Athena Eyster, David Evans, and Lauri Pesonen as well as discussions and manuscript feedback from Francis Macdonald, Yuem Park, Toby Rivers, Sarah Slotznick, Justin Strauss, and Yiming Zhang. Bruce Buffett provided insights on the implications of a stagnant lid regime for the generation of the geomagnetic field. Many participants in the Nordic Paleomagnetism Workshop have contributed to the compilation and evaluation of the pole list utilized herein. Particular acknowledgement goes to David Evans for maintaining and distributing the compiled pole lists. GPlates, and in particular the pyGPlates API, was utilized in this work \citep{Muller2018b}. Figures were made using Matplotlib \citep{Hunter2007a} in conjunction with cartopy \citep{Met-Office2010a} and pmagpy \citep{Tauxe2016a} within an interactive Python environment \citep{Perez2007a}. The chapter text as well as code, data, and reconstructions used in this paper are openly available and licensed for any form of reuse with attribution (CC BY 4.0) in this repository: \url{https://github.com/Swanson-Hysell-Group/Laurentia_Paleogeography} which is also archived on Zenodo (https://doi.org/10.5281/zenodo.5129624).

>>>>

%%%%%%%%%%%%% Acknowledgements %%%%%%%%%%%%%
\footnotesize
\subsection*{Acknowledgements}
This work was supported by NSF CAREER Grant EAR-1847277. The manuscript benefited from reviews from Athena Eyster, David Evans, and Lauri Pesonen as well as discussions and manuscript feedback from Francis Macdonald, Yuem Park, Toby Rivers, Sarah Slotznick, Justin Strauss, and Yiming Zhang. Bruce Buffett provided insights on the implications of a stagnant lid regime for the generation of the geomagnetic field. Many participants in the Nordic Paleomagnetism Workshop have contributed to the compilation and evaluation of the pole list utilized herein. Particular acknowledgement goes to David Evans for maintaining and distributing the compiled pole lists. GPlates, and in particular the pyGPlates API, was utilized in this work \citep{Muller2018b}. Figures were made using Matplotlib \citep{Hunter2007a} in conjunction with cartopy \citep{Met-Office2010a} and pmagpy \citep{Tauxe2016a} within an interactive Python environment \citep{Perez2007a}. The chapter text as well as code, data, and reconstructions used in this paper are openly available and licensed for any form of reuse with attribution (CC BY 4.0) in this repository: \url{https://github.com/Swanson-Hysell-Group/Laurentia_Paleogeography} which is also archived on Zenodo (https://doi.org/10.5281/zenodo.5129927).
